---
title: "FDI_BCP_behavioal analysis"
author: "Liang Tong"
date: today
format: 
  revealjs: 
    slide-number: true
editor: visual
execute: 
  eval: true
  echo: false
  warning: false
  message: false
fontsize: 19pt
---

# To update list

1.  median response time for each participant & condition

2.  liner maxed effect models (Omer?)

3.  contract/muscle/Participant 不同

# Intro of dataset

load the behavioral data matrix should contain one row for each trial

col 1: subject num

col 2: block num

col 3: contrast (high or low contrast)

col 4: muscle (1=FDI, 2=BCP)

col 5: trial outcome (**1=correct, 2=error**, 4=no response, 3 too early, **6 slow**, 5 wrong muscle) (3 4 5 can't use)

col 6: RT in sec

col 7: evshowtime =\[\] % 0.2sec additional time after response

col 8: participant response, 1 = left, 2 = right 0= on response

col 9: correct response, 1 = left, 2 = right

col 10: first tilt used for SSVEP

```{r 1}
#https://r-graph-gallery.com/220-basic-ggplot2-histogram.html#binSize
library(ggplot2)
library(dplyr)
library(hrbrthemes)
library(viridis)
#https://statsandr.com/blog/anova-in-r/
library(palmerpenguins)# for ANOVA
#https://cran.r-project.org/web/packages/data.table/vignettes/datatable-intro.html
library(data.table)# for large dataset

data = read.csv('G:/My Drive/Phd/Stage1/BCPvsFDI/E1data_polit/EMG_bahivour/TL_ALL_ForR.csv')

# convert to data table format, good for large size
DT <- as.data.table(data)
```

# Analysis chain

-   (slow) correct vs (slow) wrong: C / W / SC / SW
-   **different RT lock ? \<0.8/ 0.6-1.8/1.5-2**

Globle

-   Accuracy : \_Acc

-   Reaction time: \_RT

Variable

-   FDI vs BCP : FDI / BCP

-   contract level: Easy(0.14) / Hard(0.07)

-   Hand : Left / Right

individual different

-   **different subject: \_sub1...6**

-   **different block: \_blo1...8**

# Accuracy analysis \_ACC

## FDI Vs BCP（Hypo: BCP lower acc than FDI. cuz CoM）

no clear difference in acc between FDI and BCP

```{r}
#extract data
FDI_C <- DT[muscle_used=="1",
                     sum( (respLR == corrLR &  perf != "5" &  perf != "3" &  perf != "4"))] 

BCP_C <- DT[muscle_used=="2",
                     sum( (respLR == corrLR &  perf != "5" &  perf != "3" &  perf != "4"))] 

FDI_W <- DT[muscle_used=="1",
                     sum( (respLR != corrLR &  perf != "5" &  perf != "3" &  perf != "4"))] 

BCP_W <- DT[muscle_used=="2",
                     sum( (respLR != corrLR &  perf != "5" &  perf != "3" &  perf != "4"))] 

FDI_Acc <- FDI_C/(FDI_C+FDI_W)
BCP_Acc <- BCP_C/(BCP_C+BCP_W)

print('FDI acc is:')
FDI_Acc
print('BCP acc is:')
BCP_Acc

```

## Contract level E / H (Hypo Easy has higher ACC)

proved

```{r}
#extract data
E_C <- DT[contrast=="0.14" , #easy correct
                     sum( (respLR == corrLR &  perf != "5" &  perf != "3" &  perf != "4"))] 

H_C <- DT[contrast=="0.07" , #hard correct
                     sum( (respLR == corrLR &  perf != "5" &  perf != "3" &  perf != "4"))] 

E_W <- DT[contrast=="0.14" , #easy wrong
                     sum( (respLR != corrLR &  perf != "5" &  perf != "3" &  perf != "4"))] 

H_W <- DT[muscle_used=="2", #hard Wrong
                     sum( (respLR != corrLR &  perf != "5" &  perf != "3" &  perf != "4"))] 

E_Acc <- E_C/(E_C+E_W)
H_Acc <- H_C/(H_C+H_W)

print('Easy acc is:')
E_Acc
print('Hard acc is:')
H_Acc
```

## Left/Right hand L/R (Hypo left hand acc lower)

all right handed; no big difference

```{r}
#extract data
L_C <- DT[respLR=="1" , #Left correct
                     sum( (respLR == corrLR &  perf != "5" &  perf != "3" &  perf != "4"))] 

R_C <- DT[respLR=="2" , #right correct
                     sum( (respLR == corrLR &  perf != "5" &  perf != "3" &  perf != "4"))] 

L_W <- DT[respLR=="1" , #left wrong
                     sum( (respLR != corrLR &  perf != "5" &  perf != "3" &  perf != "4"))] 

R_W <- DT[muscle_used=="2", #right Wrong
                     sum( (respLR != corrLR &  perf != "5" &  perf != "3" &  perf != "4"))] 

L_Acc <- L_C/(L_C+L_W)
R_Acc <- R_C/(R_C+R_W)

print('Left acc is:')
L_Acc
print('Right acc is:')
R_Acc
```

## Summary

-   no clear difference in acc between FDI and BCP 82%

-   Easy has higher ACC 89% vs 80%

-   no clear difference in acc between left and right hand 82%

# RT Analysis \_RT

## FDI Vs BCP（Hypo: BCP faster than FDI）

## Overall

RT difference between BCP and FDI

plot histgram (no observious difference)

**!!!not normlized, can't show the difference**

```{r}
#extract data 
FDI_RT <- DT[muscle_used=="1"  ]$rt
BCP_RT <- DT[muscle_used=="2"  ]$rt


# Build dataset to plot
data_FDIBCP_RT <- data.frame(
  type = c( rep("FDI", length(FDI_RT)), rep("BCP", length(BCP_RT)) ),
  value = c( FDI_RT, BCP_RT )
)

# Represent it
p <- data_FDIBCP_RT %>%
  ggplot( aes(x=value, fill=type)) +
    geom_histogram( binwidth=0.05,color="#e9ecef", alpha=0.6, position = 'identity') +
    scale_fill_manual(values=c("#69b3a2", "#404080")) +
    theme_ipsum() +
    labs(fill="")+
    xlim(c(0, 2))

p
```

quick check using a t-test

!! There's significance difference

```{r}
t.test(FDI_RT, BCP_RT)
```

boxplot

```{r}
# Plot
data_FDIBCP_RT %>%
  ggplot( aes(x=type, y=value, fill=type)) +
    geom_boxplot() +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    theme_ipsum() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11)
    ) +
    ggtitle("A boxplot with jitter") +
    xlab("")
```

## Correct (C+S)

same when only look at correct trial

```{r}
#extract data 
FDI_RT_C <- DT[muscle_used=="1" & respLR == corrLR &  perf != "5" &  perf != "3" &  perf != "4"] $ rt
BCP_RT_C <- DT[muscle_used=="2"& respLR == corrLR & perf != "5" &  perf != "3" &  perf != "4"] $ rt


# Build dataset to plot
data_FDIBCP_RT_C <- data.frame(
  type = c( rep("FDI_C", length(FDI_RT_C)), rep("BCP_C", length(BCP_RT_C)) ),
  value = c( FDI_RT_C, BCP_RT_C )
)

# Represent it
p <- data_FDIBCP_RT_C %>%
  ggplot( aes(x=value, fill=type)) +
    geom_histogram( binwidth=0.05,color="#e9ecef", alpha=0.6, position = 'identity') +
    scale_fill_manual(values=c("#69b3a2", "#404080")) +
    theme_ipsum() +
    labs(fill="")+
    xlim(c(0, 2))

p
```

run t-test

still significant difference

```{r}
t.test(FDI_RT_C, BCP_RT_C)
```

## Wrong (W)

For wrong trial only

```{r}
#extract data 
FDI_RT_W <- DT[muscle_used=="1" & respLR != corrLR &  perf != "5" &  perf != "3" &  perf != "4"] $ rt
BCP_RT_W <- DT[muscle_used=="2" & respLR != corrLR &  perf != "5" &  perf != "3" &  perf != "4"] $ rt


# Build dataset to plot
data_FDIBCP_RT_W <- data.frame(
  type = c( rep("FDI_C", length(FDI_RT_W)), rep("BCP_C", length(BCP_RT_W)) ),
  value = c( FDI_RT_W, BCP_RT_W )
)

# Represent it
p <- data_FDIBCP_RT_W %>%
  ggplot( aes(x=value, fill=type)) +
    geom_histogram( binwidth=0.08,color="#e9ecef", alpha=0.6, position = 'identity') +
    scale_fill_manual(values=c("#69b3a2", "#404080")) +
    theme_ipsum() +
    labs(fill="")+
    xlim(c(0, 2))

p
```

t-test

still difference in wrong trials

```{r}
t.test(FDI_RT_W, BCP_RT_W)
```

## **Proof: BCP is 20-30ms faster than FDI only in correct trials**

## Contract level E / H (Hypo low slower than high contract)

## Overall

low contrast level has a slower RT

```{r}
#extract data
E_RT <- DT[contrast=="0.14"  ]$rt
H_RT <- DT[contrast=="0.07"  ]$rt


# Build dataset to plot
data_EH_RT <- data.frame(
  type = c( rep("High contrast", length(E_RT)), rep("Low contrast", length(H_RT)) ),
  value = c(E_RT, H_RT )
)

# Represent it
p <- data_EH_RT %>%
  ggplot( aes(x=value, fill=type)) +
    geom_histogram( binwidth=0.05,color="#e9ecef", alpha=0.6, position = 'identity') +
    scale_fill_manual(values=c("#69b3a2", "#404080")) +
    theme_ipsum() +
    labs(fill="")+
    xlim(c(0, 2))

p
```

## Correct(C+S)

```{r}

#extract data
E_RT_C <- DT[contrast=="0.14"& respLR == corrLR &  perf != "5" &  perf != "3" &  perf != "4" ]$rt
H_RT_C <- DT[contrast=="0.07"& respLR == corrLR &  perf != "5" &  perf != "3" &  perf != "4" ]$rt


# Build dataset to plot
data_EH_RT_C <- data.frame(
  type = c( rep("High contrast", length(E_RT_C)), rep("Low contrast", length(H_RT_C)) ),
  value = c(E_RT_C, H_RT_C )
)

# Represent it
p <- data_EH_RT_C %>%
  ggplot( aes(x=value, fill=type)) +
    geom_histogram( binwidth=0.05,color="#e9ecef", alpha=0.6, position = 'identity') +
    scale_fill_manual(values=c("#69b3a2", "#404080")) +
    theme_ipsum() +
    labs(fill="")+
    xlim(c(0, 2))

p
```

```{r}
t.test(E_RT_C, H_RT_C)
```

## Wrong (W)

```{r}
#extract data
E_RT_W <- DT[contrast=="0.14"& respLR != corrLR &  perf != "5" &  perf != "3" &  perf != "4" ]$rt
H_RT_W <- DT[contrast=="0.07"& respLR != corrLR &  perf != "5" &  perf != "3" &  perf != "4" ]$rt


# Build dataset to plot
data_EH_RT_W <- data.frame(
  type = c( rep("High contrast", length(E_RT_W)), rep("Low contrast", length(H_RT_W)) ),
  value = c(E_RT_W, H_RT_W )
)

# Represent it
p <- data_EH_RT_W %>%
  ggplot( aes(x=value, fill=type)) +
    geom_histogram( binwidth=0.05,color="#e9ecef", alpha=0.6, position = 'identity') +
    scale_fill_manual(values=c("#69b3a2", "#404080")) +
    theme_ipsum() +
    labs(fill="")+
    xlim(c(0, 2))

p
```

```{r}

t.test(E_RT_W, H_RT_W)
```

## Proof: Low(Hard) slower RT , more symmetric, High(Easy) more left screw;

## Left/Right hand L/R (Hypo left hand slower)

## Overall

```{r}
#extract data
L_RT <- DT[respLR=="1"  ]$rt#left hand
R_RT <- DT[respLR=="2"  ]$rt


# Build dataset to plot
data_LR_RT <- data.frame(
  type = c( rep("Left hand", length(L_RT)), rep("Right hand", length(R_RT)) ),
  value = c(L_RT, R_RT )
)

# Represent it
p <- data_LR_RT %>%
  ggplot( aes(x=value, fill=type)) +
    geom_histogram( binwidth=0.05,color="#e9ecef", alpha=0.6, position = 'identity') +
    scale_fill_manual(values=c("#69b3a2", "#404080")) +
    theme_ipsum() +
    labs(fill="")+
    xlim(c(0, 2))

p
```

**left is around 80ms slower than right (all right hand user)**

```{r}
t.test(L_RT, R_RT)
```

## Correct(C+S)

```{r}
#extract data
L_RT_C <- DT[respLR=="1" & respLR == corrLR &  perf != "5" &  perf != "3" &  perf != "4"  ]$rt#left hand
R_RT_C <- DT[respLR=="2" & respLR == corrLR &  perf != "5" &  perf != "3" &  perf != "4"  ]$rt


# Build dataset to plot
data_LR_RT_C <- data.frame(
  type = c( rep("Left hand", length(L_RT_C)), rep("Right hand", length(R_RT_C)) ),
  value = c(L_RT_C, R_RT_C )
)

# Represent it
p <- data_LR_RT_C %>%
  ggplot( aes(x=value, fill=type)) +
    geom_histogram( binwidth=0.05,color="#e9ecef", alpha=0.6, position = 'identity') +
    scale_fill_manual(values=c("#69b3a2", "#404080")) +
    theme_ipsum() +
    labs(fill="")+
    xlim(c(0, 2))

p
```

For correct 45ms right hand faster!!

```{r}
t.test(L_RT_C, R_RT_C)
```

## Wrong (W)

```{r}
#extract data
L_RT_W <- DT[respLR=="1" & respLR != corrLR &  perf != "5" &  perf != "3" &  perf != "4"  ]$rt#left hand
R_RT_W <- DT[respLR=="2" & respLR != corrLR &  perf != "5" &  perf != "3" &  perf != "4"  ]$rt


# Build dataset to plot
data_LR_RT_W <- data.frame(
  type = c( rep("Left hand", length(L_RT_W)), rep("Right hand", length(R_RT_W)) ),
  value = c(L_RT_W, R_RT_W )
)

# Represent it
p <- data_LR_RT_W %>%
  ggplot( aes(x=value, fill=type)) +
    geom_histogram( binwidth=0.05,color="#e9ecef", alpha=0.6, position = 'identity') +
    scale_fill_manual(values=c("#69b3a2", "#404080")) +
    theme_ipsum() +
    labs(fill="")+
    xlim(c(0, 2))

p
```

For wrong trial 120ms left hand slower

```{r}
t.test(L_RT_W, R_RT_W)
```

## Summary

-   hist is not normalized, need to find a better plot (CDF??)

-   correct RT is faster than Wrong RT

-   BCP is 20-30ms faster than FDI only in correct trials

-   Low(Hard) slower RT , more symmetric, High(Easy) more left screw;

-   left is around 80ms (45 correct 120 for wrong) slower than right response (all right hand user)
